Physcraper: a python package for continual update of evolutionary estimates using the Open Tree of Life

### 2020-08-13 2-body.Rmd
updating results

We will illustrate the utility of Physcraper in here with two use-case scenarios. One in which the user is interested in a particular group. Another one in which the user is interested in a particular phylogeny.
A tutorial as well as illustrated examples of commands for every step needed to perform a Physcraper analysis are available elsewhere.

@@

@@

Research was supported by the grant "Sustaining the Open Tree of Life", National Science Foundation ABI No. 1759838, and ABI No. 1759846.
Compute time was provided by the Multi-Environment Research Computer for Exploration and Discovery (MERCED) cluster from the University of California, Merced (UCM), supported by the NSF Grant No. ACI-1429783.

>>>>

We will illustrate the utility of Physcraper in here with two use-case scenarios. One in which the user is interested in a particular group. Another one in which the user is interested in a particular phylogeny.
A tutorial as well as illustrated examples of commands for every step needed to perform a Physcraper analysis are available in the documentation website.

@@

<!-- ```{bash echo= FALSE, include=FALSE, message= FALSE, results='hide'}
wget -O docs/figs/ilex-plot-tips-and-branches-1.png https://raw.githubusercontent.com/McTavishLab/physcraperex/master/docs/articles/ilex_files/figure-html/plot-tips-and-branches-1.png
``` -->

```{r ilex-updated-tree, echo=FALSE, fig.cap="A phylogenetic tree is the main result of a Physcraper analysis. In this example, Physcraper updated an alignment of 48 samples of the genus Ilex from Gottlieb et al. 2005 (black tips) and added 222 new samples from the GenBank database (red tips), corresponding to 78 new taxa, aligned the new seqeunces to the original alignment using MUSCLE and performed the phylogenetic reconstruction using RAxML.", out.width = '100%', fig.retina= 2}

knitr::include_graphics("docs/figs/ilex-plot-tips-and-branches-1.png")

```

The Physcraper updated tree has 57 original tips, representing 51 unique OTT taxa, and 222 new tips representing 78 new OTT taxa added to the original tree.

It has THIS many resolved nodes, and THIS MANY nodes with bootsrap values above 95%

The original tree has THIS MANY resolved nodes

The alignments have THIS MANY columns and THIS AMOUNT of missing data.

@@

Research was supported by the grant "Sustaining the Open Tree of Life", National Science Foundation ABI No. 1759838, and ABI No. 1759846.
Computer time was provided by the Multi-Environment Research Computer for Exploration and Discovery (MERCED) cluster from the University of California, Merced (UCM), supported by the NSF Grant No. ACI-1429783.

### 2020-08-13 docs/submission-mee-2020-08-12.tex
updating results

\textbf{Word count}: 3633

@@

@@

Research was supported by the grant ``Sustaining the Open Tree of Life'', National Science Foundation ABI No.~1759838, and ABI No.~1759846.
Compute time was provided by the Multi-Environment Research Computer for Exploration and Discovery (MERCED) cluster from the University of California, Merced (UCM), supported by the NSF Grant No.~ACI-1429783.

>>>>

\textbf{Word count}: 3698

@@

\begin{figure}
\includegraphics[width=1\linewidth]{docs/figs/ilex-plot-tips-and-branches-1} \caption{Physcraper outpus tree obtained by updating the alignment from Gottlieb *et al.* 2005}\label{fig:ilex-updated-tree}
\end{figure}

The Physcraper updated tree has 57 original tips, representing 51 unique OTT taxa, and 222 new tips representing 78 new OTT taxa added to the original tree.

It has THIS many resolved nodes, and THIS MANY nodes with bootsrap values above 95\%

The original tree has THIS MANY resolved nodes

The alignments have THIS MANY columns and THIS AMOUNT of missing data.

@@

Research was supported by the grant ``Sustaining the Open Tree of Life'', National Science Foundation ABI No.~1759838, and ABI No.~1759846.
Computer time was provided by the Multi-Environment Research Computer for Exploration and Discovery (MERCED) cluster from the University of California, Merced (UCM), supported by the NSF Grant No.~ACI-1429783.
